Study protocol

### 2021-08-20 Manuscript/S1.Protocol.Rmd
proof check

# Year filter. The framework convert it to the API specific format seamlessly.
# common logical comparators can be used, i.e. <, <=, >, >=, while dashes
# denotes inclusive date intervals. A single year restricts results to one year
# period.
year_filter <- '2010-2020'

@@

The query is passed to the `perform_search_session()` function, together with an unique identifier for the **search session** and **search query**. A session identifies a homogeneous group of complementary or alternative queries (e.g. sometimes it is easier to create two different simpler queries than a complex and long one that returns the same results).\
In our implementation we define as sessions the group of actions that includes the utilization of a search query and the subsequent iterations of manual review and automatic classification of its results.\

@@

If manually downloaded results are available, users can create the `Record` folder manually and put the data there (the file names need to contain the source name as written in the `sources` argument of `perform_search_session()`) and the function will acquire and parse them into a common format, even if split in multiple files due to download limits (e.g. `Pubmed1.nbib`, `Pubmed2.nib`, etc.). In addition of Pubmed, WOS and IEEE, this method permits to import also Embase and Scopus records, for which an API search was not yet implemented.\
Users can choose whether to perform an API search, parse already downloaded results, or both using the `actions` argument.

Note that for Pubmed, the API search may return slightly less records than a manual one due to a different query expansion algorithm (check Pubmed documentation) between the two services; therefore is advisable to perform also a manual search and put the resulting .nbib files in the `Session/Query` folder. `perform_search_session()` will acquire them seamlessly.

@@

Once the records are stored, they must be read and merged into an **annotation file** where the initial manual review of the records will be performed.\
A series of functions are available to prepare the data for the manual evaluation:

@@

	# Read record files. Will parse them if raw data downloaded manually (not
	# necessary in this case). Return a list of records, one per file.
	read_bib_files() %>%

@@

	# Order records by the relative frequency of the query terms in the
	# title + abstract text. Increases the chance of encountering relevant records at
	# the beginning of the manual classification.
	order_by_query_match(query) %>%

@@

Actually all these step are more easily performed through `create_annotation_file()`. This function can take as input either the path to record files, or the parsed records (one data frame or a list of data frames) or a group of folders where to look for files into./
In addition, it also allows to add the new records to a previous annotation file (arg `prev_records`), useful with subsequent searching sessions with different queries; previous manual classifications of records can be imported using `prev_classification`. By passing the original query to the `reorder_query` argument, the records are reordered empirically in order to increase the probability to find positive matches first.

```{r save annotation file}
# This function extract the appropriate file paths from a session journal. By
# default it passes all stored files, otherwise it can be filtered by session,
# query, and source (i.e. Pubmed, WOS, IEEE)
record_files <- extract_source_file_paths(journal)

@@

	# or parent folders, since it search for files recursively
input <- 'Records'

@@

Once created, the annotations needs to be stored in an **Annotation Session** folder which will contain all informations necessary for the automatic classification. This operation is streamlined by the `create_session()` function, which also help manage duplicated sessions.

@@

Notice that the framework is "piping" friendly and the precedent steps can be all performed in one call (which is the suggested procedure):

```{r one call}
# First create the Records/Session1/Query1 folder and put the manually
# downloaded records there if you have any. Otherwise the folders will be
# created automatically during the API search

@@

Now the annotation file is ready for manual classification of relevant and non-relevant records. The annotation file has a column called `Rev_manual`, where records needs to be classified as "positive" (y) or "negative" (n) by the user. From our experience, around 250 manually classified records are sufficient if a minimum ~20% positivity rate is maintained (see the section about model parameter optimization)./
The function `check_classification_trends()` can help to visualize the trend of the positives/negatives as the number of classified records increases./

Once the first records are labelled manually, the function `enrich_annotation_file()` will use Bayesian Additive Regression Trees (BART) to learn the labeling pattern of the user and predict the positive match probability for the unlabelled records. This is a summary of the prediction process:

- a Document Term Matrix (DTM) is created, extracting terms from the (lemmatized) title and abstract of the records and adding the authors and keywords. For each term, a 0/1 label specifies if it is present in each record. Also co-occurrying terms are added as ngrams and highly copresent terms are joined as synonyms;
- the positive records are weighted 10x more than the negative ones to improve sensitivity;
- the function models the labeling pattern using the manually reviewed records (learning step);
- after the model is created, it assigns a probability distribution of positivity to each record, labelled and unlabelled (prediction step). If the number of records is large, the prediction step is broken in chunks of 5000 records, to avoid memory saturation problems; the user will need to set up this parameter according to her machine capabilities;
- this process is repeated 10 times and the distributions are averaged to induce shrinkage of the estimates;
- the resulting distribution is summarised by its 98% interval and the unlabelled records will receive a positive/negative predicted label if their interval ends up completely in the joint interval of the positively/negatively labelled records. All the other records will be labeled as unknown (unk) and will require manual review.

The user can define parameters like the positives' weight, the number of models to average, whether to apply bootstrap resampling before each repetition, the prediction chunk size, and the prediction distribution interval range.
To use the function, the only input needed is the session name, the function will automatically identify the relevant file to make predictions on.

@@

This function will produce a new excel file which is stored in the Annotations folder of the session; the file will contain a column called `Rev_prediction_new` were the user will find records that require manual review marked by "*". These are records with uncertain labelling ("unk"), but also positive predictions and "y"/"n" predictions that contradict previous manually inputed labels (labeled as "check"). This approach allows to increase the accuracy of the predictions, since the machine learning system is set up to favor sensitivity at the expense of specificity. If the function finds prelabelled records (`Rev_previous` column) added when the Annotation file was created or passed as a further input to `enrich_annotation_file()` (`prev_classification` argument), they will be used to relabel the records marked in the `Rev_prediction_new` column.

@@

- a results summary page which reports the number of records that need manual review (which includes uncertain and unreviewed positive records or records with certain predictions which are different from previous manual labels), the changes, and the final distribution of the labels; it also shows other information like the number of terms in the DTM, the path to the parent file from which the annotation file was created, the replication number (see later). The content of this summary is also saved as a csv file in the Results folder.
- a variable importance page which list the used terms in order of the fraction of BART trees in which they were used. If more than 1 model repetition is used, a more robust score is computed taking the ratio of the mean of the term tree fraction among models and its standard deviation.
- the arguments passed to the function if different from the default, useful for reproducibility.
- a classification performance summary. The procedure may take some time and requires `cmdstan` installed on the machine. Therefore the `compute_performance` argument is set to FALSE by default.

Finally, the posterior samples produced by the Bayesian engine are stored on the disk. This feature can be turned off to save disk space, but at least the samples of the last annotation are necessary to build a new search query building (see next section).

Once the manual review of the generated annotation file is completed, the user can **rerun exactly the same function**. The reviewed annotation file will be automatically picked up and used for a new iteration of classification and review (CR). In case the number of records that require manual review is excessively high (e.g. > 250) the function need to be called setting the `stop_on_unreviewed` argument to `FALSE` to allow the classification to proceed even in the presence of unreviewed records (i.e. marked by "*") in the `Rev_prediction_new` column.

If there are no positive results (after manual review) in a CR iteration, the framework records the next iteration as a "replication". After four replication with no positive matches are done, the function will prevent another iteration and send a warning message. The user can change the replication limit; furthermore it's possible to have the function to stop if either a number (or a fraction of the total records) has been manually reviewed already, or if a certain number of positive matches have been found. These three parameter are passed to the `limits` argument which has the following structure and defaults:

@@

The result files in the Results folder are generated after the Classification phase but before the Review one, and therefore show preliminary results with still unreviewed records. The function `consolidate_results(session_name)` will update the results files to show the results after the manual review. The temporary result data is anyway stored in the respective annotations file.

@@

It's not uncommon that for the first query used in a systematic review not to be the the most effective one, especially in terms of sensitivity. We tried to address the problem by creating automatic query generation system. The solution is experimental and favors sensitivity at the expense of specificity. After a step in which a set of candidate query rules (to be joined by a OR logic) are selected, the user is asked to review them and select rules that make more sense to the topic or deselect too general rules that would generate too many results. The algorithm is, of course, not topic aware and therefore may very likely pick terms that are only casually associated with the topic of study; therefore a human review and selection is still needed.

@@

# The 'candidate_queries' contains the rules and the DMT and the labels on which
# the rules were built, which need to be passed to
# generate_rule_selection_set(). This function select the most effective (higher
# positive/negative matches delta) rules; also adds negative terms to increase
# specificity. A dataframe is generated (or automatically saved if save_path is
# set). The output proposes groups of equivalent (in terms of number of positive
# matches found) group of query, ordered by specificity; for each group the user
# needs to select the best rule by setting the selected_rule column to TRUE. The
# groups are in order of growing sensitivity/decreasing specificity, so it may
# make sense to exclude the last groups totally in order to avoid too many
# search results.

@@

One last thing to keep in mind is that the query generation algorithm is only aware of the literature collected inside the annotation file it's working on; so it will only be able to pick term combinations that identify positive matches inside an already specific set of documents, while not necessarily being discriminant from the rest of the global literature.\
Therefore, once the final query is generated it is advisable to add a piece with a AND logic to restrict the results in the scope of the general topic of interest.\
In our case, we added "AND ((antimicrobial resistance) OR (healthcare infection))" since being the global topic of our research, those terms were understandably not selected by the query generation algorithm as discriminant.\

@@

Once the new query was generated, a second search session called `Session2` was created, using the strategy described in the protocol. Due to the lower specificity of the second query, particular care was needed in managing the far larger amount of records, since manual downloading may be necessary from Pubmed, Embase, and Scopus (which usually have limits on the amount of records one can download at once), and because the automatic classification processing time increases proportionally to the number of records to label.\
It is advisable then to cosider removing iteratively the less specific rules from the query until a manageable number of records is found, considering that the probability of finding positive matches not already found by more specific queries drops exponentially.\

Once the new records are collected, `enrich_annotation_file('Session2')` can be used to perform the new CR iteration until no new positive matches are found. It may be possible that, during the first CR iteration, the number of records that require manual review is a large amount: we suggest to evaluate still not more than 250, keeping in mind to set the `stop_on_unreviewed` argument to `FALSE`.

Finally a number of function is available (check `R/Reporting.R`) to summarise and format the results. For example, `summarise_by_source()` and `summarise_sources_by_session()`, respectively for one session or a group of sessions, summarise from which scientific database the records are collected from, while `get_source_distribution()` describe the distribution of the number of common sources per record.\
`summarise_annotations()` and `summarise_annotations_by_session()` describe the results of the CR iterations, again for one or many sessions, reporting the number of positive and negative matches, the number of terms (features) used by the machine learning model, and how the labels changes between iterations.
`format_performance()` and `format_var_imp()` format the output of the respective analyses.
`plot_predictive_densities()` plots how the mixture of posterior predictive distributions of records, divided in positive, negative and to-review records, change between iterations,

# Results evaluation

A number of tools are available to evaluate the automatic classification performance.\
As said before, a result file is stored in the session folder for each CR iteration with a number of information on the classification status; remember to run `consolidate_results(session_name)` if you want these files to include also the manual review of the uncertain records.\
`compute_changes()` is a simpler function that take an annotation dataframe and computes the changes from the last annotation iteration.\
The main function for result analysis is `estimate_performance()`. The function uses a Bayesian model to estimate how the probability of a positive match drops as the lower boundary of the posterior predictive interval of each record decreases. This model allows to estimate the distribution of possibly missed positive records, which in turn permits to compute theoretical sensitivity and efficiency boundaries. Of course, the results are hypothetical since it is not possible to know the actual number of missed positive records.\
The function returns the Bayesian $R^2$ of the model (values below 85% would invalidate this analysis), the posterior sensitivity, the observed and theoretical number positives, the expected efficiency given the theoretical number of positives (that is 1 - the number of records reviewed above the number of records to review to find the predicted number of positives according to a negative hypergeometrical distribution). Also, the function plots the cumulative distribution of the observed and theoretical number of positive records.\
`extract_var_imp()` extract the most important terms used by the BART model and summarises their relevancy for the machine learning model and their statistical relevancy in a simple generalized linear model. Discrepancy between these two scores indicate a strongly non-linear effect of the terms.

@@

As many complex machine learning models, the choice of hyperparameters can greatly influence the framework performance. For a systematic review helper algorithm, we define the performance as the ability to find as many positive matches by manually labelling/reviewing as few records as possible:\

$$
Sensitivity \times Efficiency = \\
\frac{Pos.\ found}{Tot.\ pos.} \times \frac{Records\ reviewed}{Tot.\ records}
$$
We added a tool that uses a “grid search” algorithm to find the best set of hyperparameters. We tested these tools on our dataset, manually labeling the first 1200 records, ordered by simple query match.\
The first step is to create a folder where to store the file required for the search, for example *Grid Search*. Then a fully reviewed records file in the format generated by `create_annotation_file()` is necessary; this file can be put in the *Grid Search* but it is not mandatory. Once the folder and the file are ready run:

@@

* resample: whether to use bootstrapping to increase variability between the ensemble models;
* n_init: number of initial labelled records to train the machine learning model on;
* n_models: the number of models to fit and then average, in order to decrease the variance due to random sampling in the mcmc algorithm. It reduces the likelihood of extreme predictions;
* pos_mult: the oversampling rate of positive records. Useful to improve sensitivity;
* pred_quants: the distribution quantiles of each posterior prediction, used to define the uncertain records that require manual review.

Once the the grid search is performed, the function `analyse_grid_search()` can be used to analyze it's results. This function uses a partition tree analysis to identify hyperparameter sets (performance clusters) that are associated with a certain mean performance score. As said before, the default score is Sensitivity x Efficiency; alternatives are the Positive Rate (i.e., positive records found over total records), or Positive Rate x Sensitivity.\
The function produces a dataframe with the score and the cluster of each combination of parameters, the best hyperparameter set (i.e. the most efficient set among the most sensitive in the best cluster) and the best set for each cluster. Also, the function creates a plot that helps visualize the individual impact on performance of each hyperparameter.

Once chosen, the hyperparameters can be pass to `enrich_annotation_file()`.\
Mind that the grid search process may take many days even on powerful computers, so we suggest to stick to the default set of `enrich_annotation_file()`.

>>>>

# Year filter. The framework converts it to the API-specific format seamlessly.
# common logical comparators can be used, i.e. <, <=, >, >=, while dashes
# denotes inclusive date intervals. A single year restricts results to one year
# period.
year_filter <- '2010-2020'

@@

The query is passed to the `perform_search_session()` function, together with an unique identifier for the **search session** and **search query**. A session identifies a homogeneous group of complementary or alternative queries (e.g. sometimes it is easier to create two different simpler queries than a complex and long one that returns the same results).\
In our implementation, we define as sessions the group of actions that includes the utilization of a search query and the subsequent iterations of manual review and automatic classification of its results.\

@@

If manually downloaded results are available, users can create the `Record` folder manually and put the data there (the file names need to contain the source name as written in the `sources` argument of `perform_search_session()`), and the function will acquire and parse them into a common format, even if split in multiple files due to download limits (e.g. `Pubmed1.nbib`, `Pubmed2.nib`, etc.). In addition to Pubmed, WOS and IEEE, this method permits to import also Embase and Scopus records, for which an API search was not yet implemented.\
Using the `actions` argument, users can choose whether to perform an API search, parse already downloaded results, or both.

Note that for Pubmed, the API search may return slightly fewer records than a manual one due to a different query expansion algorithm (check Pubmed documentation) between the two services; therefore is advisable to perform also a manual search and put the resulting .nbib files in the `Session/Query` folder. `perform_search_session()` will acquire them seamlessly.

@@

Once the records are stored, they must be read and merged into an **annotation file** where the initial manual review will be performed.\
A series of functions are available to prepare the data for the manual evaluation:

@@

	# Read record files. Will parse them if raw data is downloaded manually (not
	# necessary in this case). Return a list of records, one per file.
	read_bib_files() %>%

@@

	# Order records by the relative frequency of the query terms in the title +
	# abstract text. Increases the chance of encountering relevant records at the
	# beginning of the manual classification.
	order_by_query_match(query) %>%

@@

All these steps are more easily performed through `create_annotation_file()`. This function can take as input either the path to record files, or the parsed records (one data frame or a list of data frames) or a group of folders where to look for files into./
In addition, it also allows adding the new records to a previous annotation file (arg `prev_records`). This is useful with subsequent searching sessions with different queries; previous manual classifications can be imported using `prev_classification`. By passing the original query to the `reorder_query` argument, the records are reordered empirically to increase the probability of finding positive matches first.

```{r save annotation file}
# This function extracts the appropriate file paths from a session journal. By
# default it passes all stored files, otherwise it can be filtered by session,
# query, and source (i.e. Pubmed, WOS, IEEE)
record_files <- extract_source_file_paths(journal)

@@

	# or parent folders, since it searches for files recursively
input <- 'Records'

@@

Once created, the annotations need to be stored in an **Annotation Session** folder, which will contain all information necessary for the automatic classification. This operation is streamlined by the `create_session()` function, which also helps manage duplicated sessions.

@@

Notice that the framework is "piping" friendly, and the precedent steps can be all performed in one call (which is the suggested procedure):

```{r one call}
# First, create the Records/Session1/Query1 folder and put the manually
# downloaded records there if there are any. Otherwise, the folders will be
# created automatically during the API search

@@

Now the annotation file is ready for the manual classification records. The annotation file has a column called `Rev_manual`, where records need to be classified as "positive" (y) or "negative" (n) matches by the user. We suggest manually labelling around 250  records, which should be sufficient if a minimum ~20% positivity rate is maintained (see the section about model hyperparameter optimization)./
The function `check_classification_trends()` can help visualize the trend of the positives/negatives as the number of classified records increases./

Once the first records are labelled manually, the function `enrich_annotation_file()` will use the Bayesian Additive Regression Trees (BART) machine learning model to learn the labelling pattern of the user and predict the positive match probability for the unlabelled records. Follows a summary of the prediction process:

- a Document Term Matrix (DTM) is created, extracting terms from the (lemmatized) title and abstract of the records and adding the authors and keywords. For each term, a 0/1 label specifies if it is present in each record. Also, co-occurring terms are added as n-grams, and highly copresent terms are joined as synonyms;
- the positive records are oversampled **10x** to improve sensitivity;
- the function models the labelling pattern using the manually labelled records (learning step);
- after the model is created, it assigns a probability distribution of positivity to each record, labelled and unlabelled (prediction step). If the number of records is large, the prediction step is broken into chunks of **5000 records**, to avoid memory saturation; the user will need to set up this parameter according to her machine capabilities;
- this process is repeated **10 times**, and the predictive distributions are averaged to induce shrinkage of the estimates (i.e., decrease the chance of outliers);
- the resulting distribution is summarised by its **98% interval**, and the unlabelled records will receive a positive/negative predicted label if their interval ends up entirely in the joint interval of the positively/negatively labelled records. All the other records will be labelled as unknown (unk) and will require manual review.

The user can define parameters like the positives' oversampling rate, the number of models to average, whether to apply bootstrap resampling before each repetition, the prediction chunk size, and the prediction distribution interval range.
To use the function, the only input needed is the session name; the function will automatically identify the relevant file to make predictions on.

@@

This function will produce a new excel file which is stored in the Annotations folder of the session; the file will contain a column called `Rev_prediction_new` where the user will find records that require manual review marked by "*". These are records with uncertain labelling ("unk"), but also positive predictions and "y"/"n" predictions that contradict previous manually input labels (labelled as "check"). This approach increases the accuracy of the predictions since the machine learning system is set up to favour sensitivity at the expense of specificity. If the function finds prelabelled records (`Rev_previous` column) added when the Annotation file was created or passed as a further input to `enrich_annotation_file()` (`prev_classification` argument), they will be used to label the records marked in the `Rev_prediction_new` column.

@@

- a results summary page reporting the number of records in need of manual review (which includes "unk", "check", and unreviewed "y" records), the changes, and the final distribution of the labels. It also shows other information like the number of terms in the DTM, the path to the parent file from which the annotation file was created, the replication number (see later). The content of this summary is also saved as a csv file in the Results folder.
- a variable importance page which list the used terms in order of the fraction of BART trees in which they were used. If more than one model repetition is used, a more robust score is computed taking the ratio of the mean of the term tree fraction among models and its standard deviation.
- the arguments passed to the function if different from the default, useful for reproducibility.
- a classification performance summary. The procedure may take some time and requires `cmdstan` installed on the machine. Therefore the `compute_performance` argument is set to FALSE by default.

Finally, the posterior samples produced by the Bayesian engine are stored on the disk. This feature can be turned off to save disk space, but at least the samples of the last annotation are necessary to build a new search query building (see next section) and for classification performance estimation.

The process of predicting labels and manually reviewing them is what defines a "classification and review (CR) iteration".

Once the manual review of the generated annotation file is completed, the user can **rerun exactly the same function**. The reviewed annotation file will be automatically picked up and used for a new CR iteration. If the number of records requiring manual review is excessively high (e.g. > 250), the function needs to be called with the `stop_on_unreviewed` argument set to `FALSE` to allow the classification to proceed even in the presence of unreviewed records in the `Rev_prediction_new` column.

If there are no positive results (after manual review) in a CR iteration, the framework records the next iteration as a "replication". After four replications with no positive matches are complete, the function will prevent another iteration and send a warning message. The user can change the replication limit; furthermore, it is possible to have the function stop if either a specified number (or a fraction) of the total records has been manually reviewed or if a certain number of positive matches have been found. These three parameters are passed to the `limits` argument, which has the following structure and defaults:

@@

The result files in the Results folder are generated after the Classification phase but before the Review one, and therefore show preliminary results with still unreviewed records. The function `consolidate_results(session_name)` will update the results files to show the results after the manual review. The temporary result data is stored anyway in the respective annotations file.

@@

It is not uncommon for the first query used in a systematic review not to be the most effective one, especially in terms of sensitivity. We tried to address the problem by creating an automatic query generation system. The solution is experimental and favours sensitivity at the expense of specificity. After a step in which a set of candidate query rules (to be joined by an OR logic) are selected, the user is asked to review them and select rules that make more sense to the topic or deselect too general rules that would generate many unspecific results. The algorithm is, of course, not topic aware and therefore may very likely pick terms that are only casually associated with the topic of study; therefore, human review and selection are still needed.

@@

# The 'candidate_queries' contains the rules and the DMT and the labels on which
# the rules were built, which need to be passed to
# generate_rule_selection_set(). This function selects the most effective
# (higher positive/negative matches delta) rules; also adds negative terms to
# increase specificity. A dataframe is generated (or automatically saved if
# save_path is set). The output proposes groups of equivalent (in terms of the
# number of positive matches found) groups of query, ordered by specificity; for
# each group, the user needs to select the best rule by setting the
# selected_rule column to TRUE. The groups are in order of growing
# sensitivity/decreasing specificity, so it may make sense to exclude the last
# groups totally in order to avoid too many search results.

@@

One last thing to keep in mind is that the query generation algorithm is only aware of the literature collected inside the annotation file. So it will only be able to pick term combinations that identify positive matches inside the already specific set of documents while not necessarily being discriminant from the rest of the global literature.\
Once the final query is generated, it is advisable to add a constraining subquery with an AND logic to restrict the results to the scope of the topic of interest.\
In our case, we added "AND ((antimicrobial resistance) OR (healthcare infection))" since being the global topic of our research, those terms were understandably not selected by the query generation algorithm as discriminant.\

@@

Once the new query was generated, a second search session called `Session2` was created, using the strategy described in the protocol. Due to the lower specificity of the second query, particular care was needed in managing the far larger amount of records since manual downloading may be necessary from Pubmed, Embase, and Scopus (which usually have limits on the amount of records one can download at once), and because the automatic classification processing time increases proportionally with the number of records to label.\
It is advisable then to consider removing the less specific rules iteratively from the query until a manageable number of records is obtained, considering that the probability of finding new positive matches not already found by more specific queries drops exponentially.\

Once the new records are collected, `enrich_annotation_file('Session2')` (or any other new session name) can be used to perform the new CR iterations. It may be possible that during the first CR iteration the number of records requiring manual review is a large amount: we suggest evaluating still not more than 250, keeping in mind to set the `stop_on_unreviewed` argument to `FALSE`.

## Result analysis and reporting

A number of tools are available to evaluate the automatic classification performance.\
As said before, a result file is stored in the session folder for each CR iteration with information on the classification status; remember to run `consolidate_results(session_name)` if you want these results to take into account the manual review of the predicted labels.\
`compute_changes()` is a simple function that take an annotation dataframe and computes the changes from the last annotation iteration.\
The primary function for result analysis is `estimate_performance()`. The function uses a Bayesian model to estimate how the probability of a positive match drops as records' lower boundary of the posterior predictive interval decreases. This model computes the cumulative distribution of possibly missed positive records, which in turn permits extraction of the engine's theoretical sensitivity and efficiency boundaries. These boundaries are worse case scenarios since it is impossible to know the number of missed positive records.\
The function returns the Bayesian $R^2$ of the model (values below 85-90% would invalidate this analysis), the posterior sensitivity, the observed and theoretical number positives, the expected efficiency given the theoretical number of positives (that is 1 - the number of records reviewed above the number of records to review to find the predicted number of positives according to a negative hypergeometrical distribution). Also, the function plots the cumulative distribution of the observed and theoretical number of positive records.\
`extract_var_imp()` extract the most relevant terms used by the BART model and summarises their relevancy for the machine learning model and their statistical relevancy in a simple generalized linear model. A discrepancy between these two scores indicates a non-linear effect of the terms.

Finally, several functions are available (check `R/Reporting.R`) to summarise and format the results. For example, `summarise_by_source()` and `summarise_sources_by_session()`, respectively for one session or a group of sessions, summarise from which scientific database the records are collected from, while `get_source_distribution()` describe the distribution of the number of common sources per record.\
`summarise_annotations()` and `summarise_annotations_by_session()` describe the results of the CR iterations, again for one or many sessions, reporting the number of positive and negative matches, the number of terms (features) used by the machine learning model, and how the labels changes between iterations.
`format_performance()` and `format_var_imp()` format the output of the similarly named analyses.
`plot_predictive_densities()` plots how the mixture of posterior predictive distributions of records, divided into positive, negative and to-review records, change between iterations,

@@

As with many complex machine learning models, the choice of hyperparameters can significantly influence the framework performance. For a systematic review helper algorithm, we define the performance as the ability to find as many positive matches by manually labelling/reviewing as few records as possible:\

$$
Sensitivity \times Efficiency = \\
\frac{Pos.\ found}{Tot.\ pos.} \times \frac{Records\ reviewed}{Tot.\ records}
$$

We added a “grid search” algorithm to find the best set of hyperparameters. We tested these tools on our dataset, manually labeling the first 1200 records, ordered by simple query match.\
The first step is to create a folder where to store the file required for the search, for example *Grid Search*. Then a fully reviewed records file in the format generated by `create_annotation_file()` is necessary; this file can be put in the *Grid Search* but it is not mandatory. Once the folder and the file are ready run:

@@

* resample: whether to use bootstrapping to increase variability between the ensemble models;
* n_init: number of initially labelled records to train the machine learning model on;
* n_models: the number of models to fit and then average to decrease the variance due to random sampling in the MCMC algorithm. It reduces the likelihood of extreme predictions;
* pos_mult: the oversampling rate of positive records. Useful to improve sensitivity;
* pred_quants: the distribution quantiles of each posterior prediction, used to define the uncertain records that require manual review.

Once the grid search is performed, the function `analyse_grid_search()` can be used to analyze its results. This function uses a partition tree analysis to identify hyperparameter sets (performance clusters) with different mean performance scores. As said before, the default score is Sensitivity x Efficiency; alternatives are the Positive Rate (i.e., positive records found over total records) or Positive Rate x Sensitivity.\
The function produces a dataframe with the score and the cluster of reference of each combination of parameters, the best hyperparameter set (i.e., the most efficient set among the most sensitive in the best cluster) and the best set for each cluster. Also, the function creates a plot to visualize the individual impact on performance of each hyperparameter.

Once chosen, the hyperparameters can be pass to `enrich_annotation_file()`.\
Mind that the grid search process may take many days, even on powerful computers, so we suggest sticking to the default set of `enrich_annotation_file()`. \
